---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# quickdraw

<!-- badges: start -->
<!-- badges: end -->

The `quickdraw` package allows you to download
and retrieve the dataset categories from the quickdraw dataset:


## Installation

You can install the released version of quickdraw from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("quickdraw")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("huizezhang-sherry/quickdraw")
```


## Data Retrieval

Data files are cached and retrieved using 
the `qd_read` function:
```{r setup}
library(quickdraw)

octopus <- qd_read("octopus")
octopus
```

The last column is a nested list which is a drawing made, it consists of the x,y coordinates for each stroke:

You can draw a pic with `qd_tidy` and `qd_draw`

```{r}
octopus %>% 
  qd_tidy(10) %>% 
  qd_draw()
```

You could also animate multiple drawings with
`qd_draw`

```{r}
octopus %>% 
  qd_tidy(sample.int(nrow(octopus), 6)) %>% 
  qd_draw(animate = TRUE)
```

