---
title: "quickdraw: an R interface to quickdraw data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{quickdraw}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The `quickdraw` package allows you to download
and retrieve the dataset categories from the quickdraw dataset:

## Data Retrieval

Data files are cached and retrieved using 
the `qd_read` function:
```{r setup}
library(quickdraw)

octopus <- qd_read("octopus")
octopus
```

The last column is a nested list which is a drawing made, it consists of the x,y coordinates for each stroke:

*You will have to properly install the R package `cloudml` and a command line tool, gsutil, for `qd_read()` to read data properly from Google Cloud Storage. To install gsutil, type `cloudml::gcloud_install()` in the console and follow the instructions.*

You can draw a pic with `qd_tidy` and `qd_draw`

```{r}
octopus %>% 
  qd_tidy(10) %>% 
  qd_draw()
```

You could also animate multiple drawings with
`qd_draw`

```{r}
octopus %>% 
  qd_tidy(sample.int(nrow(octopus), 6)) %>% 
  qd_draw(animate = TRUE)
```
